|

### 2016-06-01 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

same      <- same[!is.na(same$Scan),]
print(paste("Exact match:", nrow(same)))
print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
print(head(same,2))
diff_spec      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]

diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
print(paste("Different Spec eValue:", nrow(diff_spec)))
tail(diff_spec,3)
diff_pep      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide!=dta_merge$pepseq),]

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
tail(diff_pep,3)
```

>>>>

same      <- same[!is.na(same$Scan),]
print(paste("Exact match:", nrow(same)))
print(paste("From Docker:", names(same)[2],names(same)[3],". From PNNL:", names(same)[4],names(same)[5]))
print(head(same[order(same$`ms-gf:specevalue`, decreasing = T),],2))
diff_spec      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]

diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
print(paste("Different Spec eValue:", nrow(diff_spec)))
tail(diff_spec[order(diff_spec$`ms-gf:specevalue`, decreasing = T),],3)
diff_pep      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide!=dta_merge$pepseq),]

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
diff_scan <- nlevels(as.factor(diff_pep$Scan))
print(paste("Different ID and Spec eValue:", nrow(diff_pep), "with", diff_scan, "distict Scan numbers."))
tail(diff_pep[order(diff_pep$`ms-gf:specevalue`, decreasing = T),],3)
```
